Model

### 2019-04-17 stats/model.Rmd
infer sem knowledge with developmental so param

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
)
# 
# saveRDS(sem_know_model, "../saves/sem_know_model.rds")

>>>>

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
# )
#  
# saveRDS(sem_know_model, "../saves/sem_know_model.rds")
